|

### 2022-02-14 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
fix

TLS = FALSE
```

@@

if(!TLS){
  litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")
}

@@

Going further, we examine accepted tokens side-by-side with the original source material. We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table 2,<!-- \ref{tbl:15samplesentences} --> 50 more in the Appendix \ref{app:50samplesentences}, and the full set online. To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined). At the sentence level, we find codings accurately reflect the key events of the text. Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}

@@

Recall of critical events for ICBe and other state-of-the-art systems are shown in Table 3.<!-- \ref{tbl:casestudy196} --> ICBe records 8 of 10 critical events identified by the case history. It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors. It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
CaseStudy196_ft %>%
  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
    flextable::width( j = 1, width=0.5)  %>%
    flextable::width( j = 2, width=1.25)  %>%
    flextable::width( j = 3, width=0.5) %>%
    flextable::width( j = 4, width=1.1) %>%
    flextable::width( j = 5, width=1) %>%
    flextable::width( j = 6, width=0.75) %>%
    flextable::width( j = 7, width=0.65)

@@

Recall of critical events is shown in Table 4 below.<!-- \ref{tbl:casestudy426} --> ICBe records 10 of 14 critical events identified by the case history. It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N. peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC. These details were under-textualized in the ICB narrative. Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets. As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events. Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event. The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila. The MIDs incident-level dataset includes possible coverage of 4 events. MIDs episode-level data incorporates possible coverage of 6 events. Finally, Dyadic ICB data cover 7 events.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
CaseStudy426_ft  %>%
  flextable::set_caption("DRC Civil War ground truth and event data") %>%
      width(j=1, width=0.5) %>%
      width(j=2, width=0.75) %>%
      width(j=3, width=0.3) %>%
      width(j=4, width=0.65) %>%
      width(j=5, width=1.0) %>%
      width(j=6, width=0.5) %>%
      width(j=7, width=0.75) %>%
      width(j=8, width=0.75) %>%
      width(j=9, width=0.5) %>%
      width(j=10, width=0.5)

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:50samplesentences}

>>>>

@@

litreview_ft <- litreview_ft %>% ftExtra::colformat_md(j = 4, part="body")

@@

Going further, we examine accepted tokens side-by-side with the original source material. We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tab:fifteensamplesentences}, 50 more in the Appendix \ref{app:50samplesentences}, and the full set online. To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined). At the sentence level, we find codings accurately reflect the key events of the text. Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.

```{r fifteensamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}

@@

Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tab:casestudy196}. ICBe records 8 of 10 critical events identified by the case history. It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors. It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.

@@

```{r casestudy196, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
CaseStudy196_ft %>%
  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
    flextable::width( j = 1, width=0.5)  %>%
    flextable::width( j = 2, width=1.25)  %>%
    flextable::width( j = 3, width=0.5) %>%
    flextable::width( j = 4, width=1.1) %>%
    flextable::width( j = 5, width=1) %>%
    flextable::width( j = 6, width=0.75) %>%
    flextable::width( j = 7, width=0.65)

@@

Recall of critical events is shown in Table \ref{tab:casestudy426} below. ICBe records 10 of 14 critical events identified by the case history. It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N. peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC. These details were under-textualized in the ICB narrative. Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets. As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events. Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event. The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila. The MIDs incident-level dataset includes possible coverage of 4 events. MIDs episode-level data incorporates possible coverage of 6 events. Finally, Dyadic ICB data cover 7 events.

```{r casestudy426, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
CaseStudy426_ft  %>%
  flextable::set_caption("DRC Civil War ground truth and event data") %>%
      width(j=1, width=0.5) %>%
      width(j=2, width=0.75) %>%
      width(j=3, width=0.3) %>%
      width(j=4, width=0.65) %>%
      width(j=5, width=1.0) %>%
      width(j=6, width=0.5) %>%
      width(j=7, width=0.75) %>%
      width(j=8, width=0.75) %>%
      width(j=9, width=0.5) %>%
      width(j=10, width=0.5)

@@

```{r fiftysamplesentences, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:fiftysamplesentences}
